A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2020-05-21 manuscript.Rmd
mention screenshot of rstudio in docker earlier
bump release number

[^1]: To comment on our paper, please add an issue to the GitHub repository of our paper: [https://github.com/aaronpeikert/reproducible-research/issues](https://github.com/aaronpeikert/reproducible-research/issues).
[^doi]: [https://guides.github.com/activities/citable-code/](https://guides.github.com/activities/citable-code/)
[^sub]: We created an release for the submission: [https://github.com/aaronpeikert/reproducible-research/releases/tag/v0.1.1-submission](https://github.com/aaronpeikert/reproducible-research/releases/tag/v0.1.1-submission)

@@

>>>>

[^1]: To comment on our paper, please add an issue to the GitHub repository of our paper: [https://github.com/aaronpeikert/reproducible-research/issues](https://github.com/aaronpeikert/reproducible-research/issues).
[^doi]: [https://guides.github.com/activities/citable-code/](https://guides.github.com/activities/citable-code/)
[^sub]: We created an release for the submission: [https://github.com/aaronpeikert/reproducible-research/releases/tag/v0.2.0-submission](https://github.com/aaronpeikert/reproducible-research/releases/tag/v0.2.0-submission)

@@

Figure \@ref(fig:rstudio-in-docker) shows a screenshot of the result.
